Emulating Comparative Oncology Trials with Real-world Evidence Studies (ENCORE): Process Development and Methodological Considerations for Oncology Real-World Data

### 2025-10-22 manuscript/manuscript.tex
Manuscript updated

\textbf{Authors}: Janick Weberpals\textsuperscript{1}, Sebastian
Schneeweiss\textsuperscript{1}, Kenneth L. Kehl\textsuperscript{2},
Donna R. Rivera\textsuperscript{3}, Pallavi
Mishra-Kalyani\textsuperscript{3}, Catherine C.
Lerro\textsuperscript{3}, Erin Larkins\textsuperscript{4}, Sonia
Singh\textsuperscript{4*}, Preeti Narayan\textsuperscript{4}, Richard
Curley\textsuperscript{4}, Georg Hahn\textsuperscript{1}, Priyanka
Anand\textsuperscript{1}, Yanina Natanzon\textsuperscript{5}, Andrew J.
Belli\textsuperscript{6}, Ching-Kun Wang\textsuperscript{6}, Jenna
Collins\textsuperscript{7}\textbf{,} Jonathan
Kish\textsuperscript{7}\textbf{,} Janet Espirito\textsuperscript{8},
Nicholas J Robert\textsuperscript{8}, Robert J.
Glynn\textsuperscript{1}, Shirley V. Wang\textsuperscript{1}

@@

\ul{\textbf{Abstract word count:}} 228 words / 250 words

@@

\ul{\textbf{Funding Statement:}} This project was supported by an FDA
BAA contract with contract number 75F40122C00181.

@@

\emph{Manuscript last updated: 2025-07-26 11:39:19.945045}

>>>>

\textbf{Authors}: Janick Weberpals\textsuperscript{1}, Sebastian
Schneeweiss\textsuperscript{1}, Kenneth L. Kehl\textsuperscript{2},
Donna R. Rivera\textsuperscript{3*}, Pallavi
Mishra-Kalyani\textsuperscript{3}, Catherine C.
Lerro\textsuperscript{3*}, Erin Larkins\textsuperscript{4}, Preeti
Narayan\textsuperscript{4}, Richard Curley\textsuperscript{3}, Georg
Hahn\textsuperscript{1}, Priyanka Anand\textsuperscript{1}, Yanina
Natanzon\textsuperscript{5}, Andrew J. Belli\textsuperscript{6},
Ching-Kun Wang\textsuperscript{6}, Jenna
Collins\textsuperscript{7}\textbf{,} Jonathan
Kish\textsuperscript{7}\textbf{,} Janet Espirito\textsuperscript{8},
Nicholas J Robert\textsuperscript{8}, Robert J.
Glynn\textsuperscript{1}, Shirley V. Wang\textsuperscript{1}

@@

\ul{\textbf{Abstract word count:}} 224 words / 250 words

@@

\ul{\textbf{FDA Disclaimer:}}This article reflects the views of the
authors and should not be construed to represent FDA's views or
policies.

\ul{\textbf{Funding Statement:}} This project was supported by the
Oncology Center of Excellence, Food and Drug Administration (FDA) of the
U.S. Department of Health and Human Services (HHS) as part of a contract
{[}75F40122C00181{]}. The contents are those of the author(s) and do not
necessarily represent the official views of, nor an endorsement by
FDA/HHS, or the U.S. Government.

@@

\emph{Manuscript last updated: 2025-10-22 19:30:06.576264}
